Fitness tracking reveals task-specific associations between memory, mental health, and exercise

### 2021-10-08 paper/main.tex
working on results section (writing up behavioral results) [WIP]

We expected (and found) that the general trends and
tendancies in the behavioral data followed previously reported
behaviors from similar tasks that had been utilized in prior work.

In Figure~\ref{fig:immediate_behavior}, we summarize participants'
behaviors on four immediate (short term) memory tests: free recall
(Fig.~\ref{fig:immediate_behavior}a), a naturalistic recall task
(Fig.~\ref{fig:immediate_behavior}b), a foreign language vocabularly
learning task (Fig.~\ref{fig:immediate_behavior}c), and a spatial
learning task (Fig.~\ref{fig:immediate_behavior}d).

>>>>

Performance on the foreign language flashcards task (immediate:
Fig.~\ref{fig:immediate_behavior}c; delayed:
Fig.~\ref{fig:delayed_behavior}c) varied substantially across
participants, and did not show any clear serial position effects.
Participants also displayed substantial variation in performance on
the spatial learning task (Fig.~\ref{fig:immediate_behavior}d).  In
general, participants reported the shape's positions more accurately
when there were fewer shapes.  However, both the baseline estimation accuracy and
the rate of decrease in accuracy as a function of increasing number of
memorized locations varied substantially across participants.
